Scheduling and Amortization for MPC

### 2022-01-22 paper_SIMD.tex
Update writeup description of raise_dim() and drop_dim()

$\mathit{raise\_dim}(A[i_1,...,i_k],i_{k+1})$ is defined as follows. It results in a new {k+1}-dimensional array $A'$ where for every $0\le i_{k+1} < I_{k+1}$, $A'[i_1,...,i_k,i_{k+1}] = A[i_1,...,i_k]$. We add the new dimension at the end arbitrarily, it can be added at any position, e.g., before $i_1$, etc. Adding $n$ dimensions is trivially extended as a composition of $n$ $\mathit{raise\_dim}$ that each adds a single dimension.

@@

$\mathit{drop\_dim}(A[i_1,...,i_k,i_{k+1}])$ produces a k-dimensional array $A'$ where $A'[i_1,...,i_k] = A'[i_1,...,i_k,I_{k+1}-1]$. In our analysis, dimensions are always dropped at the end, and again, one can define dropping $n$ dimensions as a composition of $n$ $\mathit{drop\_dim}$.

>>>>

$\mathit{raise\_dim}(A[i_1,...,i_k],i_j)$ is defined as follows.  It results in a new {k+1}-dimensional array $A'$ where for every $0 \le i_{k} < I_{k+1}$, $A'[i_1, \ldots, i_j, \ldots, i_k] = A[i_1, \ldots, i_k]$. Adding $n$ dimensions is trivially extended as a composition of $n$ $\mathit{raise\_dim}$ that each adds a single dimension.

@@

$\mathit{drop\_dim}(A[i_1,\ldots, i_j, \ldots,i_k], i_j)$ produces a k-dimensional array $A'$ where $A'[i_1,\ldots,i_k] = A'[i_1,\ldots, I_j-1, \ldots,i_k]$. In our analysis, dimensions are always dropped at the end, and again, one can define dropping $n$ dimensions as a composition of $n$ $\mathit{drop\_dim}$.

\ben{I'm not sure if I wrote up the above paragraphs correctly -- the idea is that we're just copying values to extend over dimension $j$ or only retain its last elements.  The current writeup implies that $1 < j < k$ though, which isn't always true.  Python implementations of $\mathit{raise\_dim}()$ and $\mathit{drop\_dim}()$ can be found here: \url{https://github.com/milana2/ParallelizationForMPC/blob/master/compiler/compiler/motion_backend/reference_implementations.py}}
